Exploring the Shadows of Terror: The Influence of Terrorism on Public Opinion and Democratic Values

### 2024-02-13 outputs/paper/paper.qmd
another figure added

library(tidyverse)
library(readxl)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(psych)
library(patchwork)
```

@@

>>>>

# install.packages("tidyverse")
# install.packages("readxl")
# install.packages("ggplot2")
# install.packages("ggpubr")
# install.packages("dplyr")

library(tidyverse)
library(readxl) # reading excel files
library(ggplot2)
library(ggpubr) # for gg rearrange
library(dplyr)
```

@@

Another figure

```{r}
#| echo: false
#| warning: false
#| message: false

##### Fig3A.1 Overall ##### 
library(broom)
library(dotwhisker)
library(cowplot)
library(metafor)
############################
# 1) outgroup dataset
dat_outgroup <- dat[dat$PA_Category == 10 |
                      dat$PA_Category == 99, ]
# 2) conservative shift dataset
dat_conservatism <- dat[dat$PA_Category == 5 |
                          dat$PA_Category == 6 |
                          dat$PA_Category == 7 |
                          dat$PA_Category == 8 |
                          dat$PA_Category == 9 |
                          dat$PA_Category == 11, ]
# 3) rally-around-the-flag dataset
dat_rally <- dat[dat$PA_Category == 1 |
                   dat$PA_Category == 2 |
                   dat$PA_Category == 3 |
                   dat$PA_Category == 4, ]
######################################################
dat_outgroup$TerrorType2[dat_outgroup$Type==0] <- "No ideology"
dat_outgroup$TerrorType2[dat_outgroup$Type==1] <- "Islamist"
dat_outgroup$TerrorType2[is.na(dat_outgroup$TerrorType2)] <- "Other"
dat_outgroup$TerrorType2 <- as.factor(dat_outgroup$TerrorType2)
#convert into dummy variables
dat_outgroup$Islam <- ifelse(dat_outgroup$TerrorType2=="Islamist", yes=1, no=0)
dat_outgroup$No_Ideology <- ifelse(dat_outgroup$TerrorType2=="No ideology", yes=1, no=0)
dat_outgroup$Other_Ideology <- ifelse(dat_outgroup$TerrorType2=="Other", yes=1, no=0)
################################
dat_outgroup$Exp <- ifelse(dat_outgroup$TypeStudy==1, yes=1, no=0)
dat_outgroup$QuasiLong <- ifelse(dat_outgroup$TypeStudy==2 | 
                                   dat_outgroup$TypeStudy==4, yes=1, no=0)
dat_outgroup$Corr <- ifelse(dat_outgroup$TypeStudy==3, yes=1, no=0)
################################
dat_outgroup$Sample[dat_outgroup$GeneralPop==1] <- "General"
dat_outgroup$Sample[dat_outgroup$StudentPop==1] <- "Student"
dat_outgroup$Sample[is.na(dat_outgroup$Sample)] <- "Convenience"
dat_outgroup$Sample <- as.factor(dat_outgroup$Sample)
dat_outgroup$General <- ifelse(dat_outgroup$Sample=="General", yes=1, no=0)
dat_outgroup$Student <- ifelse(dat_outgroup$Sample=="Student", yes=1, no=0)
dat_outgroup$Convenience <- ifelse(dat_outgroup$Sample=="Convenience", yes=1, no=0)
################################
dat_outgroup$US <- ifelse(dat_outgroup$Country=="US", yes=1, no=0)
dat_outgroup$Israel <- ifelse(dat_outgroup$Country=="Israel", yes=1, no=0)
dat_outgroup$Other_c <- ifelse(dat_outgroup$US==0 
                               & dat_outgroup$Israel==0, yes=1, no=0)
############################
dat_outgroup$TargetSim[dat_outgroup$OA_Similarity==2] <- "A lot"
dat_outgroup$TargetSim[dat_outgroup$OA_Similarity==1] <- "A bit"
dat_outgroup$TargetSim[dat_outgroup$OA_Similarity==0] <- "No"
dat_outgroup$TargetSim <- as.factor(dat_outgroup$TargetSim)
#convert into dummy variables
dat_outgroup$Lot <- ifelse(dat_outgroup$TargetSim=="A lot", yes=1, no=0)
dat_outgroup$Bit <- ifelse(dat_outgroup$TargetSim=="A bit", yes=1, no=0)
dat_outgroup$No <- ifelse(dat_outgroup$TargetSim=="No", yes=1, no=0)

########################################
dat_conservatism$TerrorType2[dat_conservatism$Type==0] <- "No ideology"
dat_conservatism$TerrorType2[dat_conservatism$Type==1] <- "Islamist"
dat_conservatism$TerrorType2[is.na(dat_conservatism$TerrorType2)] <- "Other"
dat_conservatism$TerrorType2 <- as.factor(dat_conservatism$TerrorType2)
#convert into dummy variables
dat_conservatism$Islam <- ifelse(dat_conservatism$TerrorType2=="Islamist", yes=1, no=0)
dat_conservatism$No_Ideology <- ifelse(dat_conservatism$TerrorType2=="No ideology", yes=1, no=0)
dat_conservatism$Other_Ideology <- ifelse(dat_conservatism$TerrorType2=="Other", yes=1, no=0)
#############################
dat_conservatism$Exposure <- ifelse(dat_conservatism$TerrorMeasure=="Acts of violence", yes=1, no=0)
dat_conservatism$R_Exposure <- ifelse(dat_conservatism$TerrorMeasure=="Reported exposure", yes=1, no=0)
dat_conservatism$Threat <- ifelse(dat_conservatism$TerrorMeasure=="Threat", yes=1, no=0)
dat_conservatism$Emotions <- ifelse(dat_conservatism$TerrorMeasure=="Fear" | 
                                      dat_conservatism$TerrorMeasure=="Anger", yes=1, no=0)
dat_conservatism$Fear <- ifelse(dat_conservatism$TerrorMeasure=="Fear", yes=1, no=0)
dat_conservatism$Anger <- ifelse(dat_conservatism$TerrorMeasure=="Anger", yes=1, no=0)
dat_conservatism$Other_IV <- ifelse(dat_conservatism$TerrorMeasure=="Other", yes=1, no=0)
################################################################
#recode data
dat_conservatism$Design[dat_conservatism$TypeStudy==1] <- "Experiments"
dat_conservatism$Design[dat_conservatism$TypeStudy==2] <- "Quasi-Long"
dat_conservatism$Design[dat_conservatism$TypeStudy==3] <- "Correlations"
dat_conservatism$Design[dat_conservatism$TypeStudy==4] <- "Quasi-Long"
dat_conservatism$Design <- as.factor(dat_conservatism$Design)
#convert characters into dummy variables
dat_conservatism$Exp <- ifelse(dat_conservatism$TypeStudy==1, yes=1, no=0)
dat_conservatism$QuasiLong <- ifelse(dat_conservatism$TypeStudy==2 | 
                                       dat_conservatism$TypeStudy==4, yes=1, no=0)
dat_conservatism$Corr <- ifelse(dat_conservatism$TypeStudy==3, yes=1, no=0)
################################################
#recode data
dat_conservatism$Country2[dat_conservatism$Country=="US"] <- "US"
dat_conservatism$Country2[dat_conservatism$Country=="Israel"] <- "Israel"
dat_conservatism$Country2[is.na(dat_conservatism$Country2)] <- "Other"
dat_conservatism$Country2 <- as.factor(dat_conservatism$Country2)
#convert characters into dummy variables
dat_conservatism$US <- ifelse(dat_conservatism$Country=="US", yes=1, no=0)
dat_conservatism$Israel <- ifelse(dat_conservatism$Country=="Israel", yes=1, no=0)
dat_conservatism$Other_c <- ifelse(dat_conservatism$US==0 
                               & dat_conservatism$Israel==0, yes=1, no=0)
################################################

#recode data
dat_conservatism$Sample[dat_conservatism$GeneralPop==1] <- "General"
dat_conservatism$Sample[dat_conservatism$StudentPop==1] <- "Student"
dat_conservatism$Sample[is.na(dat_conservatism$Sample)] <- "Convenience"
dat_conservatism$Sample <- as.factor(dat_conservatism$Sample)
#convert characters into dummy variables
dat_conservatism$General <- ifelse(dat_conservatism$Sample=="General", yes=1, no=0)
dat_conservatism$Student <- ifelse(dat_conservatism$Sample=="Student", yes=1, no=0)
dat_conservatism$Convenience <- ifelse(dat_conservatism$Sample=="Convenience", yes=1, no=0)

################################################
set.seed(1234)
og_overall <- rma.mv(y=Fisher, V=Variance_F,
                     random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                     method = "ML")
og_overall_df <- tidy(og_overall) # create data.frame of regression results

og_overall_df <- og_overall_df %>%  #re-label variable
  relabel_predictors(overall = "Overall Fisher's Z \n Correlation Coef." )           
og_overall_plot <- dwplot(og_overall_df, #plot
                          dot_args = list(size = 3),
                          whisker_args = list(size = 1),
                          vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 1))+
  ggtitle("Outgroup Hostility") +
  scale_color_grey() +
  xlim(-0.1, .25) +
  theme(axis.title.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm"),
        axis.text.y = element_text(face = "bold",size = 14),
        axis.ticks.x=element_blank(),
        axis.text.x=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
        panel.background = element_rect(fill = "grey90",
                                        colour = "grey90"),
        panel.grid = element_line(colour = "grey60"))

##### Fig3A.2 Terror type ##### 
#fit model and plot results
set.seed(1234)
og_terror <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Islam, Other_Ideology, No_Ideology),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")

og_terror_df <- tidy(og_terror) # create data.frame of regression results

og_terror_df <- og_terror_df %>%  #re-label variable
  relabel_predictors(c(Islam = "Islamist",
                       Other_Ideology  = "Other ideology",
                       No_Ideology  = "No ideology"))
og_terror_plot <- dwplot(og_terror_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3A.3 Research Design ##### 
#fit model and plot results
set.seed(1234)
og_design <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Exp, QuasiLong, Corr),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")

og_design_df <- tidy(og_design) # create data.frame of regression results

og_design_df <- og_design_df %>%  #re-label variable
  relabel_predictors(c(Exp = "Experiment",
                       Corr  = "Cross-sectional",
                       QuasiLong  = "Other designs"))
og_design_plot <- dwplot(og_design_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3A.4 Sample  ##### 
#fit model and plot results
set.seed(1234)
og_sample <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(General, Student, Convenience),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")

og_sample_df <- tidy(og_sample) # create data.frame of regression results

og_sample_df <- og_sample_df %>%  #re-label variable
  relabel_predictors(c(General = "General population",
                       Student  = "Student sample",
                       Convenience  = "Convenience sample"))
og_sample_plot <- dwplot(og_sample_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3A.5 Geography ##### 
#fit model and plot results
set.seed(1234)
og_location <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(US, Israel, Other_c),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                    method = "ML")
og_location_df <- tidy(og_location) # create data.frame of regression results

og_location_df <- og_location_df %>%  #re-label variable
  relabel_predictors(c(US = "United States",
                       Israel  = "Israel",
                       Other_c  = "Other countries"))
og_location_plot <- dwplot(og_location_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3A.6 Guilt-by-Association ##### 
#fit model and plot results
set.seed(1234)
og_association <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Lot, Bit, No),
                      intercept=F, 
                      random = ~ 1 | ID_R/ID_ES_Unique, data=dat_outgroup,
                      method = "ML")

og_association_df <- tidy(og_association) # create data.frame of regression results

og_association_df <- og_association_df %>%  #re-label variable
  relabel_predictors(c(Lot = "Strong association",
                       Bit  = "Moderate association",
                       No  = "No association"))
og_association_plot <- dwplot(og_association_df, #plot
                           dot_args = list(size = 2),
                           whisker_args = list(size = 0.5),
                           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  ggtitle("Guilt-By-Association") +
  scale_y_discrete(position = "left") +
  scale_color_grey() +
  theme(axis.title=element_text(face = "bold"),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25)

##### Fig3A Outgroup Hostility Effect Sizes Plot ##### 
og_plots <- plot_grid(og_overall_plot, og_terror_plot, og_design_plot, og_sample_plot, og_location_plot,
                      og_association_plot,
                      ncol=1, nrow=6, 
                      rel_heights=c(0.8,1,1,1,1,1), align = "v")

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3B. Conservative Shift Hypothesis ##### 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3B.1 Overall ##### 
set.seed(1234)
cs_overall <- rma.mv(y=Fisher, V=Variance_F,
                     random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                     method = "ML")
cs_overall_df <- tidy(cs_overall) # create data.frame of regression results

cs_overall_df <- cs_overall_df %>% 
  relabel_predictors(c(overall = "Overall Effect Size")) #re-label variable
cs_overall_plot <- dwplot(cs_overall_df, #plot
                          dot_args = list(size = 3),
                          whisker_args = list(size = 1),
                          vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 1))+
  ggtitle("Conservative Shift") +
  scale_color_grey() +
  xlim(-0.1, .25) +
  theme(axis.title.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm"),
        axis.ticks=element_blank(),
        axis.text=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
        panel.background = element_rect(fill = "grey90",
                                        colour = "grey90"),
        panel.grid = element_line(colour = "grey60"))

##### Fig3B.2 Terror type ##### 
#fit model and plot results
set.seed(1234)
cs_terror <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Islam, Other_Ideology, No_Ideology),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                    method = "ML")

cs_terror_df <- tidy(cs_terror) # create data.frame of regression results

cs_terror_df <- cs_terror_df %>%  #re-label variable
  relabel_predictors(c(Islam = "Islamist",
                       Other_Ideology  = "Other Ideology",
                       No_Ideology  = "No Ideology"))
cs_terror_plot <- dwplot(cs_terror_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), axis.text=element_blank(), axis.ticks=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3B.3 Research Design ##### 
#fit model and plot results
set.seed(1234)
cs_design <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Exp, QuasiLong, Corr),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                    method = "ML")
cs_design_df <- tidy(cs_design) # create data.frame of regression results

cs_design_df <- cs_design_df %>%  #re-label variable
  relabel_predictors(c(Exp = "Experiments",
                       Corr  = "Cross-Sectional",
                       QuasiLong  = "Other Designs"))
cs_design_plot <- dwplot(cs_design_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), axis.text=element_blank(), 
        axis.ticks=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3B.4 Sample  ##### 
#fit model and plot results
set.seed(1234)
cs_sample <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(General, Student, Convenience),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                    method = "ML")

cs_sample_df <- tidy(cs_sample) # create data.frame of regression results

cs_sample_df <- cs_sample_df %>%  #re-label variable
  relabel_predictors(c(General = "General Population",
                       Student  = "Student Samples",
                       Convenience  = "Convenience Samples"))
cs_sample_plot <- dwplot(cs_sample_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), 
        axis.text=element_blank(), axis.ticks=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3B.5 Geography ##### 
#fit model and plot results
set.seed(1234)
cs_location <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(US, Israel, Other_c),
                      intercept=F, 
                      random = ~ 1 | ID_R/ID_ES_Unique, data=dat_conservatism,
                      method = "ML")
cs_location_df <- tidy(cs_location) # create data.frame of regression results

cs_location_df <- cs_location_df %>%  #re-label variable
  relabel_predictors(c(US = "United States",
                       Israel  = "Israel",
                       Other_c  = "Other Countries"))
cs_location_plot <- dwplot(cs_location_df, #plot
                           dot_args = list(size = 2),
                           whisker_args = list(size = 0.5),
                           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(plot.title = element_text(size = 14), 
        axis.text.y=element_blank(), axis.ticks.y=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_color_grey() +
  xlim(-0.1, .25)

##### Fig3B Conservative Shift Effect Sizes Plot ##### 
cs_plots <- plot_grid(cs_overall_plot, cs_terror_plot, cs_design_plot, cs_sample_plot, cs_location_plot, 
                      ncol=1, nrow=6, 
                      rel_heights=c(0.8,1,1,1,1,1), align = "v")

```{r fig.width=15, fig.height=16}
#| echo: false
#| warning: false
#| message: false

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3C. Rally Effects Hypothesis ##### 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
##### Fig3C.1 Overall ##### 
#recode data
dat_rally$TerrorType2[dat_rally$Type==0] <- "No ideology"
dat_rally$TerrorType2[dat_rally$Type==1] <- "Islamist"
dat_rally$TerrorType2[is.na(dat_rally$TerrorType2)] <- "Other"
dat_rally$TerrorType2 <- as.factor(dat_rally$TerrorType2)
#convert into dummy variables
dat_rally$Islam <- ifelse(dat_rally$TerrorType2=="Islamist", yes=1, no=0)
dat_rally$No_Ideology <- ifelse(dat_rally$TerrorType2=="No ideology", yes=1, no=0)
dat_rally$Other_Ideology <- ifelse(dat_rally$TerrorType2=="Other", yes=1, no=0)

####################################

#convert characters into dummy variables
dat_rally$Exposure <- ifelse(dat_rally$TerrorMeasure=="Acts of violence", yes=1, no=0)
dat_rally$R_Exposure <- ifelse(dat_rally$TerrorMeasure=="Reported exposure", yes=1, no=0)
dat_rally$Threat <- ifelse(dat_rally$TerrorMeasure=="Threat", yes=1, no=0)
dat_rally$Emotions <- ifelse(dat_rally$TerrorMeasure=="Fear" | 
                                      dat_rally$TerrorMeasure=="Anger", yes=1, no=0)
dat_rally$Fear <- ifelse(dat_rally$TerrorMeasure=="Fear", yes=1, no=0)
dat_rally$Anger <- ifelse(dat_rally$TerrorMeasure=="Anger", yes=1, no=0)
dat_rally$Other_IV <- ifelse(dat_rally$TerrorMeasure=="Other", yes=1, no=0)

############################

#recode data
dat_rally$Design[dat_rally$TypeStudy==1] <- "Experiments"
dat_rally$Design[dat_rally$TypeStudy==2] <- "Quasi-Long"
dat_rally$Design[dat_rally$TypeStudy==3] <- "Correlations"
dat_rally$Design[dat_rally$TypeStudy==4] <- "Quasi-Long"
dat_rally$Design <- as.factor(dat_rally$Design)
#convert characters into dummy variables
dat_rally$Exp <- ifelse(dat_rally$TypeStudy==1, yes=1, no=0)
dat_rally$QuasiLong <- ifelse(dat_rally$TypeStudy==2 | 
                                dat_rally$TypeStudy==4, yes=1, no=0)
dat_rally$Corr <- ifelse(dat_rally$TypeStudy==3, yes=1, no=0)

####################################

#recode data
dat_rally$Sample[dat_rally$GeneralPop==1] <- "General"
dat_rally$Sample[dat_rally$StudentPop==1] <- "Student"
dat_rally$Sample[is.na(dat_rally$Sample)] <- "Convenience"
dat_rally$Sample <- as.factor(dat_rally$Sample)
#convert characters into dummy variables
dat_rally$General <- ifelse(dat_rally$Sample=="General", yes=1, no=0)
dat_rally$Student <- ifelse(dat_rally$Sample=="Student", yes=1, no=0)
dat_rally$Convenience <- ifelse(dat_rally$Sample=="Convenience", yes=1, no=0)
####################################
#recode data
dat_rally$Country2[dat_rally$Country=="US"] <- "US"
dat_rally$Country2[dat_rally$Country=="Israel"] <- "Israel"
dat_rally$Country2[is.na(dat_rally$Country2)] <- "Other"
dat_rally$Country2 <- as.factor(dat_rally$Country2)
#convert characters into dummy variables
dat_rally$US <- ifelse(dat_rally$Country=="US", yes=1, no=0)
dat_rally$Israel <- ifelse(dat_rally$Country=="Israel", yes=1, no=0)
dat_rally$Other_c <- ifelse(dat_rally$US==0 
                                   & dat_rally$Israel==0, yes=1, no=0)
####################################

set.seed(1234)
rf_overall <- rma.mv(y=Fisher, V=Variance_F,
                     random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                     method = "ML")
rf_overall_df <- tidy(rf_overall) # create data.frame of regression results

rf_overall_df <- rf_overall_df %>% 
  relabel_predictors(c(overall = "Overall Effect Size")) #re-label variable
rf_overall_plot <- dwplot(rf_overall_df, #plot
                          dot_args = list(size = 3),
                          whisker_args = list(size = 1),
                          vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 1))+
  ggtitle("Rally Effects") +
  scale_color_grey() +
  xlim(-0.1, .25) +
  theme(axis.title.x=element_blank(),
        plot.margin=grid::unit(c(0,0,0,0), "mm"),
        axis.ticks=element_blank(),
        axis.text=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
        panel.background = element_rect(fill = "grey90",
                                        colour = "grey90"),
        panel.grid = element_line(colour = "grey60"))

##### Fig3C.2 Terror type ##### 
#fit model and plot results
set.seed(1234)
rf_terror <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Islam, Other_Ideology, No_Ideology),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                    method = "ML")
rf_terror_df <- tidy(rf_terror) # create data.frame of regression results

rf_terror_df <- rf_terror_df %>%  #re-label variable
  relabel_predictors(c(Islam = "Islamist",
                       Other_Ideology  = "Other Ideology",
                       No_Ideology  = "No Ideology"))
rf_terror_plot <- dwplot(rf_terror_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  ylab("Ideology") +
  scale_y_discrete(position = "right") +
  scale_color_grey() +
  theme(axis.text=element_blank(), axis.ticks=element_blank(), 
        axis.title.y=element_text(face = "bold", size = 14),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25)

##### Fig3C.3 Research Design ##### 
#fit model and plot results
set.seed(1234)
rf_design <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(Exp, QuasiLong, Corr),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                    method = "ML")
rf_design_df <- tidy(rf_design) # create data.frame of regression results

rf_design_df <- rf_design_df %>%  #re-label variable
  relabel_predictors(c(Exp = "Experiments",
                       Corr  = "Cross-Sectional",
                       QuasiLong  = "Other Designs"))
rf_design_plot <- dwplot(rf_design_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text=element_blank(), axis.ticks=element_blank())+
  ylab("Design") +
  scale_y_discrete(position = "right") +
  scale_color_grey() +
  theme(axis.text=element_blank(), axis.ticks=element_blank(), 
        axis.title.y=element_text(face = "bold", size = 14),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25)

##### Fig3C.4 Sample  ##### 
#fit model and plot results
set.seed(1234)
rf_sample <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(General, Student, Convenience),
                    intercept=F, 
                    random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                    method = "ML")
rf_sample_df <- tidy(rf_sample) # create data.frame of regression results

rf_sample_df <- rf_sample_df %>%  #re-label variable
  relabel_predictors(c(General = "General Population",
                       Student  = "Student Samples",
                       Convenience  = "Convenience Samples"))
rf_sample_plot <- dwplot(rf_sample_df, #plot
                         dot_args = list(size = 2),
                         whisker_args = list(size = 0.5),
                         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  theme(axis.text=element_blank(), axis.ticks=element_blank())+
  ylab("Sample") +
  scale_y_discrete(position = "right") +
  scale_color_grey() +
  theme(axis.text=element_blank(), axis.ticks=element_blank(), 
        axis.title.y=element_text(face = "bold", size = 14),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25)

##### Fig3C.5 Geography ##### 
#fit model and plot results
set.seed(1234)
rf_location <- rma.mv(y=Fisher, V=Variance_F, mods = cbind(US, Israel, Other_c),
                      intercept=F, 
                      random = ~ 1 | ID_R/ID_ES_Unique, data=dat_rally,
                      method = "ML")
rf_location_df <- tidy(rf_location) # create data.frame of regression results

rf_location_df <- rf_location_df %>%  #re-label variable
  relabel_predictors(c(US = "United States",
                       Israel  = "Israel",
                       Other_c  = "Other Countries"))
rf_location_plot <- dwplot(rf_location_df, #plot
                           dot_args = list(size = 2),
                           whisker_args = list(size = 0.5),
                           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2, size = 0.7)) +
  ylab("Country") +
  scale_y_discrete(position = "right") +
  scale_color_grey() +
  theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), 
        axis.title.y=element_text(face = "bold", size = 14),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))+
  xlim(-0.1, .25)

##### Fig3C Rally Effects Effect Sizes Plot ##### 
rf_plots <- plot_grid(rf_overall_plot, rf_terror_plot, rf_design_plot, rf_sample_plot, rf_location_plot,
                      ncol=1, nrow=6, 
                      rel_heights=c(0.8,1,1,1,1,1), align = "v")

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
################################# FIGURE 3 ###############################
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #

ggarrange(og_plots, cs_plots, rf_plots,
          align = "hv",
          ncol = 3, nrow = 1,
          widths=c(2.2,1.3,1.4)) #arrange all plots
